A Unified Treatment of Tractability for Approximation Problems Defined on Hilbert Spaces

### 2023-07-18 GeneralizedTractability2023July17.tex
Fred M2 2023 Mac Updates

\title{A Unified Treatment of Tractability of Approximation Problems Defined on Hilbert Spaces}

@@

Define
\[
i(\varepsilon,\vp):= \lfloor C_{\vp}\, T(\varepsilon^{-1},1,\vp)\rfloor +1, \quad
i(\infty,\vp) =\lfloor C_{\vp}\, T(0,1,\vp)\rfloor +1.
\]
Thus, it follows by \eqref{eq:lambda_K_strong3} that $\lambda_{i(\varepsilon,\vp),d} \le \varepsilon$.
Note furthermore that we always have
\[
i(\varepsilon,\vp)\le C_{\vp}\, T(\varepsilon^{-1},1,\vp)+1 \le C_{\vp} T(\lambda_{i(\varepsilon,\vp),d}^{-1},1,\vp)+1, \qquad \forall \varepsilon > 0, \ d \in \mathbb{N},
\]
since
$T(\cdot,1, \vp)$ is non-decreasing.

@@

For a fixed $c$ and $d$, define
\begin{equation} \label{eq:nstardef}
	\varepsilon^{-1}_{\max}(d,c) := \max(V_c - d,\lambda_{\max}^{-1}), \qquad n^*(d,c) : = n(\varepsilon^{-1}_{\max}(d,c),d,c) \le h(cT(\varepsilon^{-1}_{\max}(d,c),d)) +1.
\end{equation}
\peter{[PETER: We do not have $\lambda_{\max}$ anymore, and it could be unbounded, right? But I think this can be fixed: I keep the black (current) version, and provide a purple (new) version below, with only few changes. Please check carefully whether we can use the purple one.]}
By varying $\varepsilon^{-1}$ in the interval $[\varepsilon^{-1}_{\max}(d,c),\infty)$,  the integer $n(\varepsilon,d,c)$ attains, \peter{by Assumption \eqref{eq:Tlim},} all values greater than or equal to $n^*(d,c)$.  Thus, by \eqref{eq:nedcbound},
\begin{align}
		n &\le h(cT(\lambda^{-1}_{n,d},d)) \qquad  \forall n \ge n^*(d,c), \label{eq:subhTneq}\\
		\nonumber
		\frac{1}{h(2 cT(\lambda^{-1}_{n,d},d)) } & \le \frac{1}{[h(cT(\lambda^{-1}_{n,d},d))]^{2}}  \le \frac 1{n^2}   \qquad  \forall n \ge n^*(d,c) \qquad \text{by \eqref{eq:h_cond}}. \\
		\intertext{Combining this inequality with the upper bound on $n^*(d,c)$ yields}
		\nonumber
		S_{2c} & =\sup_{d\in\naturals}  \, \sum_{i=1}^\infty \frac1{h(2cT(\lambda_{i,d}^{-1},d))} \\
		\nonumber
		&  = \sup_{d\in\naturals} \left [
		\sum_{i=1}^{n^*(d,c)-1} \frac1{h(2cT(\lambda_{i,d}^{-1},d))}
		+ \sum_{i=n^*(d,c)}^\infty \frac1{h(2cT(\lambda_{i,d}^{-1},d))}
		\right]\\
		 \nonumber
		 & \le \sup_{d\in\naturals} \left [
\frac{n^*(d,c)-1}{h(2cT(\lambda_{\max}^{-1},d))}
+ \sum_{i=1}^\infty \frac1{n^2}
\right]
 \qquad \text{by \eqref{eq:subhTneq}}\\
 \label{eq:lastone}
		 & \le \sup_{d\in\naturals} \left [
		 \frac{ h(cT(\varepsilon^{-1}_{\max}(d,c),d))}{h(2cT(\lambda_{\max}^{-1},d))}
		\right] + \frac{\pi^2}{6}
		\qquad \text{by \eqref{eq:nstardef}.}
\end{align}

Note that
\[
\varepsilon^{-1}_{\max}(d,c) = \max(V_c - d,\lambda_{\max}^{-1})
= \begin{cases} V_c - d \le V_c, & d \in \{1, \ldots, d^*_c : = \lfloor V_c - \lambda_{\max}^{-1} \rfloor\}, \\
\lambda_{\max}^{-1}, & d \in \{d^*_c+1, \ldots\}.
\end{cases}
\]
Recalling that $T$ is non-decreasing in its arguments, this implies that
\begin{align*}
    \MoveEqLeft{\sup_{d\in\naturals} \,
		 \frac{ h(cT(\varepsilon^{-1}_{\max}(d,c),d))}{h(2cT(\lambda_{\max}^{-1},d))}}\\
  &\le \max \left \{
  \sup_{d \in \{1, \ldots, d^*_c\}} \,
		 \frac{ h(cT(\varepsilon^{-1}_{\max}(d,c),d))}{h(2cT(\lambda_{\max}^{-1},d))},
  \sup_{d\in \{d^*_c+1, \ldots \}} \,
		 \frac{ h(cT(\varepsilon^{-1}_{\max}(d,c),d))}{h(2cT(\lambda_{\max}^{-1},d))}
  \right \} \\
  & \le \max \left \{
  \sup_{d \in \{1, \ldots, d^*_c\}}  \,
		 \frac{ h(cT(V_c,d))}{h(2cT(\lambda_{\max}^{-1},d))}
  ,
  \sup_{d\in \{d^*_c+1, \ldots \}}  \,
		 \frac{ h(cT(\lambda_{\max}^{-1},d))}{h(2cT(\lambda_{\max}^{-1},d))}
  \right \}
  \\
  & \le \max \left \{
		 \frac{ h(cT(V_c,d^*_c))}{h(2cT(\lambda_{\max}^{-1},1))},
  \sup_{d\in \{d^*_c+1, \ldots \}}  \,
		 \frac{ h(cT(\lambda_{\max}^{-1},d))}{[h(cT(\lambda_{\max}^{-1},d))]^2}
  \right \} \\
  & = \max \left \{
		 \frac{ h(cT(V_c,d^*_c))}{h(2cT(\lambda_{\max}^{-1},1))},
		 \frac{1}{h(cT(\lambda_{\max}^{-1},d_c^*+1))}
  \right \} \\
  & < \infty.
\end{align*}
Combining this bound with the upper bound on $S_c$ in \eqref{eq:lastone} establishes the finiteness of $S_{2c}$ and completes the proof of the necessary condition.
This concludes the proof of Theorem \ref{thm:subhT}.

\peter{***ALTERNATIVE VERSION OF THE LAST PART OF THE PROOF - PLEASE CHECK (essentially just by replacing $\lambda_{\max}$ by something different***}

\peter{
For a fixed $c$ and $d$, define
\begin{equation} \label{eq:nstardef}
	\varepsilon^{-1}_{\max}(d,c) := \max(V_c - d,\lambda_{1,d}^{-1}), \qquad n^*(d,c) : = n(\varepsilon^{-1}_{\max}(d,c),d,c) \le h(cT(\varepsilon^{-1}_{\max}(d,c),d)) +1.
\end{equation}
By varying $\varepsilon^{-1}$ in the interval $[\varepsilon^{-1}_{\max}(d,c),\infty)$,  the integer $n(\varepsilon,d,c)$ attains, \peter{by Assumption \eqref{eq:Tlim},} all values greater than or equal to $n^*(d,c)$.  Thus, by \eqref{eq:nedcbound},
\begin{align}
		n &\le h(cT(\lambda^{-1}_{n,d},d)) \qquad  \forall n \ge n^*(d,c), \label{eq:subhTneq}\\
		\nonumber
		\frac{1}{h(2 cT(\lambda^{-1}_{n,d},d)) } & \le \frac{1}{[h(cT(\lambda^{-1}_{n,d},d))]^{2}}  \le \frac 1{n^2}   \qquad  \forall n \ge n^*(d,c) \qquad \text{by \eqref{eq:h_cond}}. \\
		\intertext{Combining this inequality with the upper bound on $n^*(d,c)$ yields}
		\nonumber
		S_{2c} & =\sup_{d\in\naturals}  \, \sum_{i=1}^\infty \frac1{h(2cT(\lambda_{i,d}^{-1},d))} \\
		\nonumber
		&  = \sup_{d\in\naturals} \left [
		\sum_{i=1}^{n^*(d,c)-1} \frac1{h(2cT(\lambda_{i,d}^{-1},d))}
		+ \sum_{i=n^*(d,c)}^\infty \frac1{h(2cT(\lambda_{i,d}^{-1},d))}
		\right]\\
		 \nonumber
		 & \le \sup_{d\in\naturals} \left [
\frac{n^*(d,c)-1}{h(2cT(\lambda_{1,d}^{-1},d))}
+ \sum_{i=1}^\infty \frac1{n^2}
\right]
 \qquad \text{by \eqref{eq:subhTneq}}\\
 \label{eq:lastone}
		 & \le \sup_{d\in\naturals} \left [
		 \frac{ h(cT(\varepsilon^{-1}_{\max}(d,c),d))}{h(2cT(\lambda_{1,d}^{-1},d))}
		\right] + \frac{\pi^2}{6}
		\qquad \text{by \eqref{eq:nstardef}.}
\end{align}

Note that
\[
\varepsilon^{-1}_{\max}(d,c) = \max(V_c - d,\lambda_{1,d}^{-1})
= \begin{cases} V_c - d \le V_c, & d \in \{1, \ldots, d^*_c : = \lfloor V_c - \lambda_{1,d}^{-1} \rfloor\}, \\
\lambda_{1,d}^{-1}, & d \in \{d^*_c+1, \ldots\}.
\end{cases}
\]
Note that it follows from above that we always have $d^*_c\le \lfloor V_c \rfloor$

Recalling that $T$ is non-decreasing in its arguments, this implies that
\begin{align*}
    \MoveEqLeft{\sup_{d\in\naturals} \,
		 \frac{ h(cT(\varepsilon^{-1}_{\max}(d,c),d))}{h(2cT(\lambda_{1,d}^{-1},d))}}\\
  &\le \max \left \{
  \sup_{d \in \{1, \ldots, d^*_c\}} \,
		 \frac{ h(cT(\varepsilon^{-1}_{\max}(d,c),d))}{h(2cT(\lambda_{1,d}^{-1},d))},
  \sup_{d\in \{d^*_c+1, \ldots \}} \,
		 \frac{ h(cT(\varepsilon^{-1}_{\max}(d,c),d))}{h(2cT(\lambda_{1,d}^{-1},d))}
  \right \} \\
  & \le \max \left \{
  \sup_{d \in \{1, \ldots, d^*_c\}}  \,
		 \frac{ h(cT(V_c,d))}{h(2cT(\lambda_{1,d}^{-1},d))}
  ,
  \sup_{d\in \{d^*_c+1, \ldots \}}  \,
		 \frac{ h(cT(\lambda_{1,d}^{-1},d))}{h(2cT(\lambda_{1,d}^{-1},d))}
  \right \}
  \\
  & \le \max \left \{
		 \frac{ h(cT(V_c,d^*_c))}{h(2cT(\lambda_{1,d}^{-1},1))},
  \sup_{d\in \{d^*_c+1, \ldots \}}  \,
		 \frac{ h(cT(\lambda_{1,d}^{-1},d))}{[h(cT(\lambda_{1,d}^{-1},d))]^2}
  \right \} \\
  & = \max \left \{
		 \frac{ h(cT(V_c,d^*_c))}{h(2cT(\lambda_{1,d}^{-1},1))},
		 \frac{1}{h(cT(\lambda_{1,d}^{-1},d_c^*+1))}
  \right \} \\
  & \le \max \left \{
		 \frac{ h(cT(V_c,\lfloor d^*_c \rfloor))}{1},
		 1
  \right \} \\
  & = h(cT(V_c,\lfloor V_c \rfloor))
		  \\
  & < \infty,
\end{align*}
where we used that $h(\cdot)$ is always at least 1. Combining this bound with the upper bound on $S_c$ in \eqref{eq:lastone} establishes the finiteness of $S_{2c}$ and completes the proof of the necessary condition.
This concludes the proof of Theorem \ref{thm:subhT}.
}

\qed
\end{proof}

\begin{example}[Weak Tractability]
	Suppose that
	\[
	T(\varepsilon^{-1},d,s,t) = \max(1,\varepsilon^{-1})^s + d^t, \quad \forall \varepsilon,s,t > 0, \, d \in \naturals, \qquad h(x) = \exp(x) \quad \forall x \ge 0.
	\]
	Then Theorem \ref{thm:subhT} implies that
	\[\lim_{\varepsilon^{-1}+d\rightarrow \infty} \frac{\log( \comp(\varepsilon,d))}{\varepsilon^{-s}+d^t} = 0
	\iff
	 \sup_{d\in\naturals}  \, \sum_{i=1}^\infty \exp(-c\, (\min\{1,\lambda_{i,d}\}^{s} + d^t )) <\infty \qquad \forall c > 0.
	\]
	The expression on the left is the notion of $(s,t)$-weak tractability \peter{introduced in \cite{SW15}}, and the condition on the right was derived in \peter{\cite[Theorem 3.1]{WW17}}.  Weak tractability corresponds to $(s,t)=(1,1)$, and uniform weak tractability corresponds to the case when a problem is weakly tractable for all positive $s$ and $t$.
\end{example}

@@

Define $\theUB: \naturals \to \natzero \cup \{\infty\}$
\begin{equation} \label{eq:Mddef}
    \theUB(d) := \begin{cases}
        \min\{n \in \natzero : \lambda_{n+1,d} \le \theM(d)\}, & \theM(d) > 0, \\
        \infty, & \theM(d) = 0.
    \end{cases}
\end{equation}
Also, for each $d \in \naturals$ define the set
\begin{equation} \label{eq:hIdef}
\hI = \mathcal{I}_d :=\begin{cases}
\emptyset, & \theUB(d) = 0, \\
\{1,\ldots, \theUB(d)\}, & 0 < \theUB(d) < \infty, \\
\naturals, & \theUB(d) = \infty.
\end{cases}
\end{equation}
\peter{[I have no idea why the $\mathcal{I}_d$ is not displayed correctly above.]}
From the definition of $\theUB(d)$ it follows that $(\lambda_{i,d}^{-1},d) \in \Omega  \iff i \in \hI_d$, and
\begin{equation} \label{eq:comprestr}
  \comp(\varepsilon,d) \begin{cases}
= 0, & \theUB(d) = 0, \\
    \in \hI_d, & \theUB(d) > 0,
\end{cases}
\qquad \forall (\varepsilon^{-1},d) \in \Omega.
\end{equation}

@@

We note that it may be possible to define $\Omega$ such that $\lambda_{1,d} > \theM(d)$
\peter{[should it not be $\lambda_{1,d} \le \theM(d)$ ?]}
for all $d \in \naturals$. In this case, $\theUB(d) = 0$ for all $d \in \naturals$, the equivalent conditions for (strong) tractability are trivially satisfied, and the zero algorithm satisfies the error tolerance.

@@

Moreover, given that $T$ is increasing in its arguments, we have the following equivalent expression for the complexity via
\eqref{eq:comp_def} \peter{[Again, no clue why the $\mathcal{I}_d$ is not displayed correctly below]}:
\begin{align} %\label{eq:comp_equiv}
	\nonumber
	\comp(\varepsilon, d) & = \min \{n \in \hI_d : \lambda_{n+1, d} \le \varepsilon\} \qquad \text{by \eqref{eq:comprestr}} \\
	\nonumber
	& = \min \biggl\{n \in \hI_d : \frac{1}{T(\lambda_{n+1,d}^{-1},\thed,\vp)}\le \frac{1}{T(\varepsilon^{-1},\thed,\vp) }\biggr\} \qquad  \forall \thed\in \naturals\\
	\nonumber
	& \le  \min \biggl\{n \in \hI_d : n \ge N - 1 + T(\varepsilon^{-1},\thed,\vp) \sum_{i=N}^{\theUB(d)} \frac{1}{T(\lambda_{i, d}^{-1},\thed,\vp)} \biggr\} \;  \forall  \thed, \ 1 \le N \le \theUB(d) \\
 \nonumber
 & \hspace{20ex}\text{by \eqref{eq:implicate_a_rest}.}
 \intertext{
 This last statement holds for all $N \le \theUB(d)$ because $n \ge N$ automatically in the expression above.  Thus,}
 \comp(\varepsilon,d)
	& \le  T(\varepsilon^{-1},\thed,\vp) \Biggl [\frac{N}{T(\varepsilon^{-1},\thed,\vp)}  +  \sum_{i=N}^{\theUB(d)} \frac{1}{T(\lambda_{i, d}^{-1},\thed,\vp)} \Biggr] \quad \forall  \thed,\ 1 \le N \le \theUB(d). \label{eq:compUP_rest}
\end{align}

@@

For $(\varepsilon^{-1}, d) \in \Omega$, define the positive integers
\[
i(\varepsilon,\vp):= \lfloor C_{\vp}\, T(\varepsilon^{-1},1,\vp)\rfloor +1, \quad
i(\infty,\vp) =  \lfloor C_{\vp}\, T(0,1,\vp)\rfloor +1 \ge 1 .
\]
Thus, it follows by \eqref{eq:lambda_K_strong4} that $\lambda_{i(\varepsilon,\vp),d} \le \varepsilon$
for any  $(\varepsilon^{-1}, d) \in \Omega$.
Note furthermore that we always have
\[
i(\varepsilon,\vp)\le C_{\vp}\, T(\varepsilon^{-1},1,\vp)+1 \le C_{\vp} T(\lambda_{i(\varepsilon,\vp),d}^{-1},1,\vp)+1, \qquad  \forall \varepsilon > \theM(d), \ d \in \mathbb{N},
\]
since
$T(\cdot,1, \vp)$ is non-decreasing.

For $\varepsilon$ taking on all values in $(\theM(d),\infty)$, $i(\varepsilon,\vp)$ takes on (at least) all values in
\[
I_{d,\vp}:=\begin{cases}
\emptyset, & i(\theM(d),\vp) = i(\infty,\vp) \\
\{i(\infty,\vp),\ldots, i(\theM(d),\vp)-1\}, & \theM(d) > 0, \\
\{i(\infty,\vp), i(\infty,\vp) + 1, \ldots\}, & \theM(d) = 0.
\end{cases}
\]
So,
\[
i\le  C_{\vp} T(\lambda_{i,d}^{-1},1,\vp)+1, \qquad \forall i\in I_{d,\vp},  \ d \in \naturals.
\]
This implies via our technical assumption \eqref{eq:ptauassume} that
\begin{gather}
\nonumber
 K_{\vp,\tau}\,T (\lambda_{i,d}^{-1},1,\tau \vp) \ge
 [T(\lambda_{i,d}^{-1},1, \vp)]^\tau
 \ge
  \left[\frac{(i-1)}{C_{\vp}}\right]^\tau \qquad \forall i\in I_{d,\vp},  \ d \in \naturals, \\
  \label{eq:rest_strong_ineq}
 \frac{1}{T (\lambda_{i,d}^{-1},1,\tau \vp)} \le
\frac{K_{\vp,\tau}\, C_{\vp}^\tau}{(i-1)^\tau}\qquad \forall i \in I_{d,\vp} \setminus\{1\}, \ d \in \naturals .
\end{gather}

@@

\item If $\theUB(d) \ge L_{\tau\vp}$ and $\theM(d) = 0$, then $\{L_{\tau\vp},  L_{\tau\vp} + 1, \ldots \} \subseteq I_{d,\vp} \setminus \{1\}$.

\item If $\theUB(d) \ge L_{\tau\vp}$ and $\theM(d) >0$, then \eqref{eq:Mddef} and \eqref{eq:lambda_K_strong4} imply that
\[
\lambda_{i(\theM(d),\vp),d} \le \lambda_{\theUB(d)+1,d} \le \theM(d) < \lambda_{\theUB(d),d}.
\]
\peter{
[PETER. In the above chain of inequalities, I am not quite sure that I understand the first one. Is it because...
\begin{itemize}
    \item $\lambda_{i(\varepsilon,\vp),d)} \le \varepsilon$ for all $\varepsilon>\theM(d)$, and so it must also hold in the limit for $\varepsilon$ tending to $\theM(d)$, and
    \item $\theUB (d) +1$ is the smallest index such that $\lambda_{\theUB (d) +1} \le \theM(d)$ ?
\end{itemize}]

}
This means that $\theUB(d) \le i(\theM(d),\vp)-1$.  So, $\{L_{\tau\vp}, \ldots, \theUB(d)\} \subseteq I_{d,\vp} \setminus \{1\}$.

>>>>

\title{A Unified Treatment of Tractability for Approximation Problems Defined on Hilbert Spaces}

@@

For all positive $\varepsilon$, define
\begin{equation}\label{eq:iepsp}
i(\varepsilon,\vp):= \lfloor C_{\vp}\, T(\varepsilon^{-1},1,\vp)\rfloor +1, \quad
i(\infty,\vp) =\lfloor C_{\vp}\, T(0,1,\vp)\rfloor +1.
\end{equation}
Thus, it follows by \eqref{eq:lambda_K_strong3} that $\lambda_{i(\varepsilon,\vp),d} \le \varepsilon$.
Note furthermore that we always have
\[
i(\varepsilon,\vp)\le C_{\vp}\, T(\varepsilon^{-1},1,\vp)+1 \le C_{\vp} T(\lambda_{i(\varepsilon,\vp),d}^{-1},1,\vp)+1, \qquad \forall \varepsilon > 0, \ d \in \mathbb{N},
\]
since
$T(\cdot,1, \vp)$ is non-decreasing.

@@

For a fixed $c$ and $d$, define
\begin{equation} \label{eq:nstardef}
	\varepsilon^{-1}_{\max}(d,c) := \max(V_c - d,\lambda_{1,d}^{-1}), \qquad n^*(d,c) : = n(\varepsilon^{-1}_{\max}(d,c),d,c) \le h(cT(\varepsilon^{-1}_{\max}(d,c),d)) +1.
\end{equation}
By varying $\varepsilon^{-1}$ in the interval $[\varepsilon^{-1}_{\max}(d,c),\infty)$,  the integer $n(\varepsilon,d,c)$ attains, \peter{by Assumption \eqref{eq:Tlim},} all values greater than or equal to $n^*(d,c)$.  Thus, by \eqref{eq:nedcbound},
\begin{align}
		n &\le h(cT(\lambda^{-1}_{n,d},d)) \qquad  \forall n \ge n^*(d,c), \label{eq:subhTneq}\\
		\nonumber
		\frac{1}{h(2 cT(\lambda^{-1}_{n,d},d)) } & \le \frac{1}{[h(cT(\lambda^{-1}_{n,d},d))]^{2}}  \le \frac 1{n^2}   \qquad  \forall n \ge n^*(d,c) \qquad \text{by \eqref{eq:h_cond}}. \\
		\intertext{Combining this inequality with the upper bound on $n^*(d,c)$ yields}
		\nonumber
		S_{2c} & =\sup_{d\in\naturals}  \, \sum_{i=1}^\infty \frac1{h(2cT(\lambda_{i,d}^{-1},d))} \\
		\nonumber
		&  = \sup_{d\in\naturals} \left [
		\sum_{i=1}^{n^*(d,c)-1} \frac1{h(2cT(\lambda_{i,d}^{-1},d))}
		+ \sum_{i=n^*(d,c)}^\infty \frac1{h(2cT(\lambda_{i,d}^{-1},d))}
		\right]\\
		 \nonumber
		 & \le \sup_{d\in\naturals} \left [
\frac{n^*(d,c)-1}{h(2cT(\lambda_{1,d}^{-1},d))}
+ \sum_{i=1}^\infty \frac1{n^2}
\right]
 \qquad \text{by \eqref{eq:subhTneq}}\\
 \label{eq:lastone}
		 & \le \sup_{d\in\naturals} \left [
		 \frac{ h(cT(\varepsilon^{-1}_{\max}(d,c),d))}{h(2cT(\lambda_{1,d}^{-1},d))}
		\right] + \frac{\pi^2}{6}
		\qquad \text{by \eqref{eq:nstardef}.}
\end{align}

Note that
\[
\varepsilon^{-1}_{\max}(d,c) = \max(V_c - d,\lambda_{1,d}^{-1})
= \begin{cases} V_c - d \le V_c, & d \in \{1, \ldots, d^*_c : = \lfloor V_c - \lambda_{1,d}^{-1} \rfloor\}, \\
\lambda_{1,d}^{-1}, & d \in \{d^*_c+1, \ldots\},
\end{cases}
\]
and furthermore, it follows from above that we always have $d^*_c\le \lfloor V_c \rfloor$.
Recalling that $T$ is non-decreasing in its arguments, this implies that
\begin{align*}
    \MoveEqLeft{\sup_{d\in\naturals} \,
		 \frac{ h(cT(\varepsilon^{-1}_{\max}(d,c),d))}{h(2cT(\lambda_{1,d}^{-1},d))}}\\
  &\le \max \left \{
  \sup_{d \in \{1, \ldots, d^*_c\}} \,
		 \frac{ h(cT(\varepsilon^{-1}_{\max}(d,c),d))}{h(2cT(\lambda_{1,d}^{-1},d))},
  \sup_{d\in \{d^*_c+1, \ldots \}} \,
		 \frac{ h(cT(\varepsilon^{-1}_{\max}(d,c),d))}{h(2cT(\lambda_{1,d}^{-1},d))}
  \right \} \\
  & \le \max \left \{
  \sup_{d \in \{1, \ldots, d^*_c\}}  \,
		 \frac{ h(cT(V_c,d))}{h(2cT(\lambda_{1,d}^{-1},d))}
  ,
  \sup_{d\in \{d^*_c+1, \ldots \}}  \,
		 \frac{ h(cT(\lambda_{1,d}^{-1},d))}{h(2cT(\lambda_{1,d}^{-1},d))}
  \right \}
  \\
  & \le \max \left \{
		 \frac{ h(cT(V_c,d^*_c))}{h(2cT(\lambda_{1,d}^{-1},1))},
  \sup_{d\in \{d^*_c+1, \ldots \}}  \,
		 \frac{ h(cT(\lambda_{1,d}^{-1},d))}{[h(cT(\lambda_{1,d}^{-1},d))]^2}
  \right \} \\
  & = \max \left \{
		 \frac{ h(cT(V_c,d^*_c))}{h(2cT(\lambda_{1,d}^{-1},1))},
		 \frac{1}{h(cT(\lambda_{1,d}^{-1},d_c^*+1))}
  \right \} \\
  & \le \max \left \{
		 \frac{ h(cT(V_c,\lfloor d^*_c \rfloor))}{1},
		 1
  \right \} \\
  & = h(cT(V_c,\lfloor V_c \rfloor))
		  \\
  & < \infty,
\end{align*}
where we used that $h(\cdot)$ is always at least 1. Combining this bound with the upper bound on $S_c$ in \eqref{eq:lastone} establishes the finiteness of $S_{2c}$ and completes the proof of the necessary condition.
This concludes the proof of Theorem \ref{thm:subhT}.
\qed
\end{proof}

\begin{example}[Weak Tractability]
	Suppose that
	\[
	T(\varepsilon^{-1},d,s,t) = \max(1,\varepsilon^{-1})^s + d^t, \quad \forall \varepsilon,s,t > 0, \, d \in \naturals, \qquad h(x) = \exp(x) \quad \forall x \ge 0.
	\]
	Then Theorem \ref{thm:subhT} implies that
	\[\lim_{\varepsilon^{-1}+d\rightarrow \infty} \frac{\log( \comp(\varepsilon,d))}{\varepsilon^{-s}+d^t} = 0
	\iff
	 \sup_{d\in\naturals}  \, \sum_{i=1}^\infty \exp(-c\, (\min\{1,\lambda_{i,d}\}^{s} + d^t )) <\infty \qquad \forall c > 0.
	\]
	The expression on the left is the notion of $(s,t)$-weak tractability introduced in \cite{SW15}, and the condition on the right was derived in \cite[Theorem 3.1]{WW17}.  Weak tractability corresponds to $(s,t)=(1,1)$, and uniform weak tractability corresponds to the case when a problem is weakly tractable for all positive $s$ and $t$.
\end{example}

@@

Define $\theUB: \naturals \to \natzero \cup \{\infty\}$
\begin{equation} \label{eq:Mddef}
    \theUB(d) := \begin{cases}
        \min\{n \in \natzero : \lambda_{n+1,d} \le \theM(d)\}, & \theM(d) > 0, \\
        \infty, & \theM(d) = 0.
    \end{cases}
\end{equation}
Also, for each $d \in \naturals$ define the set
\begin{equation} \label{eq:hIdef}
\mathcal{I}_d :=\begin{cases}
\emptyset, & \theUB(d) = 0, \\
\{1,\ldots, \theUB(d)\}, & 0 < \theUB(d) < \infty, \\
\naturals, & \theUB(d) = \infty.
\end{cases}
\end{equation}
%\peter{[I have no idea why the $\mathcal{I}_d$ is not displayed correctly above.]}
From the definition of $\theUB(d)$ it follows that $(\lambda_{i,d}^{-1},d) \in \Omega  \iff i \in \hI_d$, and
\begin{equation} \label{eq:comprestr}
  \comp(\varepsilon,d) \begin{cases}
= 0, & \theUB(d) = 0, \\
    \in \hI_d, & \theUB(d) > 0,
\end{cases}
\qquad \forall (\varepsilon^{-1},d) \in \Omega.
\end{equation}

@@

We note that it may be possible to define $\Omega$ such that  $\lambda_{1,d} \le \theM(d)$
for all $d \in \naturals$. In this case, $\theUB(d) = 0$ for all $d \in \naturals$, the equivalent conditions for (strong) tractability are trivially satisfied, and the zero algorithm satisfies the error tolerance.

@@

Moreover, given that $T$ is increasing in its arguments, we have the following equivalent expression for the complexity via
\eqref{eq:comp_def}:
\begin{align} %\label{eq:comp_equiv}
	\nonumber
	\comp(\varepsilon, d) & = \min \{n \in \hI_d : \lambda_{n+1, d} \le \varepsilon\} \qquad \text{by \eqref{eq:comprestr}} \\
	\nonumber
	& = \min \biggl\{n \in \hI_d : \frac{1}{T(\lambda_{n+1,d}^{-1},\thed,\vp)}\le \frac{1}{T(\varepsilon^{-1},\thed,\vp) }\biggr\} \qquad  \forall \thed\in \naturals\\
	\nonumber
	& \le  \min \biggl\{n \in \hI_d : n \ge N - 1 + T(\varepsilon^{-1},\thed,\vp) \sum_{i=N}^{\theUB(d)} \frac{1}{T(\lambda_{i, d}^{-1},\thed,\vp)} \biggr\} \;  \forall  \thed, \ 1 \le N \le \theUB(d) \\
 \nonumber
 & \hspace{20ex}\text{by \eqref{eq:implicate_a_rest}.}
 \intertext{
 This last statement holds for all $N \le \theUB(d)$ because $n \ge N$ automatically in the expression above.  Thus,}
 \comp(\varepsilon,d)
	& \le  T(\varepsilon^{-1},\thed,\vp) \Biggl [\frac{N}{T(\varepsilon^{-1},\thed,\vp)}  +  \sum_{i=N}^{\theUB(d)} \frac{1}{T(\lambda_{i, d}^{-1},\thed,\vp)} \Biggr] \quad \forall  \thed,\ 1 \le N \le \theUB(d). \label{eq:compUP_rest}
\end{align}

@@

For  all $\varepsilon > 0$, define the positive integers
\[
i(\varepsilon,\vp):= \lfloor C_{\vp}\, T(\varepsilon^{-1},1,\vp)\rfloor +1, \quad
i(\infty,\vp) =  \lfloor C_{\vp}\, T(0,1,\vp)\rfloor +1 \ge 1,
\]
just as in \eqref{eq:iepsp}.
Thus, it follows by \eqref{eq:lambda_K_strong4} that
\begin{equation} \label{eq:lambdaiep}
\lambda_{i(\varepsilon,\vp),d} \le \varepsilon \qquad
 \forall (\varepsilon^{-1}, d) \in \Omega.
\end{equation}
Note furthermore that we always have
\[
i(\varepsilon,\vp)\le C_{\vp}\, T(\varepsilon^{-1},1,\vp)+1 \le C_{\vp} T(\lambda_{i(\varepsilon,\vp),d}^{-1},1,\vp)+1, \qquad  \forall \varepsilon > \theM(d), \ d \in \mathbb{N},
\]
since
$T(\cdot,1, \vp)$ is non-decreasing.

For $\varepsilon$ taking on all values in $(\theM(d),\infty)$, $i(\varepsilon,\vp)$ takes on (at least) all values in
\[
\mathscr{I}_{d,\vp}:=\begin{cases}
\emptyset, & i(\theM(d),\vp) = i(\infty,\vp), \\
\{i(\infty,\vp),\ldots, i(\theM(d),\vp)-1\}, & \theM(d) > 0, \\
\{i(\infty,\vp), i(\infty,\vp) + 1, \ldots\}, & \theM(d) = 0.
\end{cases}
\]
So,
\[
i\le  C_{\vp} T(\lambda_{i,d}^{-1},1,\vp)+1, \qquad \forall i\in \mathscr{I}_{d,\vp},  \ d \in \naturals.
\]
This implies via our technical assumption \eqref{eq:ptauassume} that
\begin{gather}
\nonumber
 K_{\vp,\tau}\,T (\lambda_{i,d}^{-1},1,\tau \vp) \ge
 [T(\lambda_{i,d}^{-1},1, \vp)]^\tau
 \ge
  \left[\frac{(i-1)}{C_{\vp}}\right]^\tau \qquad \forall i\in \mathscr{I}_{d,\vp},  \ d \in \naturals, \\
  \label{eq:rest_strong_ineq}
 \frac{1}{T (\lambda_{i,d}^{-1},1,\tau \vp)} \le
\frac{K_{\vp,\tau}\, C_{\vp}^\tau}{(i-1)^\tau}\qquad \forall i \in \mathscr{I}_{d,\vp} \setminus\{1\}, \ d \in \naturals .
\end{gather}

@@

\item If $\theUB(d) \ge L_{\tau\vp}$ and $\theM(d) = 0$, then $\{L_{\tau\vp},  L_{\tau\vp} + 1, \ldots \} \subseteq \mathscr{I}_{d,\vp} \setminus \{1\}$.

\item If $\theUB(d) \ge L_{\tau\vp}$ and $\theM(d) >0$, then \eqref{eq:Mddef} implies that $\lambda_{\theUB(d)+1,d} \le \theM(d) < \lambda_{\theUB(d),d}$.  Moreover, there must be some $\varepsilon^*$ satisfying $\theM(d) < \varepsilon^* < \lambda_{\theUB(d),d}$, such for which $\lambda_{i(\varepsilon^*,\vp)} \le \varepsilon^* < \lambda_{\theUB(d),d}$ by \eqref{eq:lambdaiep}.  Because of the ordering of the singular values, this implies that  $i(\varepsilon^*,\vp) \ge \theUB(d)+1$.  Since $i(\cdot,\vp)$ is nonincreasing, $i(\theM(b),\vp) \ge \theUB(d)+1$.
This means that $\theUB(d) \le i(\theM(d),\vp)-1$.  So, $\{L_{\tau\vp}, \ldots, \theUB(d)\} \subseteq \mathscr{I}_{d,\vp} \setminus \{1\}$.

In both the second and third cases,
\begin{align*}
S_{\tau\vp} & = \sup_{d\in\naturals} \sum_{i = L_{\tau\vp}}^{\theUB(d)} \frac{1}{T (\lambda_{i,d}^{-1},1, \tau \vp)}
\le
\sup_{d\in\naturals} \sum_{i \in \mathscr{I}_{d,\vp} \setminus\{1\} } \frac{1}{T (\lambda_{i,d}^{-1},1, \tau \vp)} \\
&  \le  K_{\vp,\tau}\, C_{\vp}^\tau
\sum_{i=2}^\infty \frac{1}{(i-1)^\tau}
 \le K_{\vp,\tau}\, C_{\vp}^\tau
\zeta (\tau)
 < \infty \qquad \text{by \eqref{eq:rest_strong_ineq},}
\end{align*}
where $\zeta$ denotes the Riemann zeta function.
